---
title: "Plotly"
output: 
  html_document:
    code_folding: hide 
    toc: true
    toc_float: true
---

# Plots of NY NOAA dataset

## Load packages and ny_noaa data

```{r}
library(tidyverse)
library(p8105.datasets)
library(plotly)
```

## Choose subset of data

```{r}
data("ny_noaa")

set.seed(10032)
part_ny_noaa = ny_noaa %>%
  separate(date, into = c("year","month","day"), sep = "-", remove = FALSE) %>%
  mutate(year = as.numeric(year),
         month = as.numeric(month),
         day = as.numeric(day),
         tmax = as.numeric(tmax)/10,
         tmin = as.numeric(tmin)/10,
         prcp = as.numeric(prcp)/10) %>%
  drop_na(tmax, tmin, prcp) %>%
  filter(year %in% 2005:2010) %>%
  sample_n(10000) 

part_ny_noaa

```


In 'ny_noaa' data, there are `r nrow(ny_noaa)` observations, which is a really huge data. So, we would like to choose part of observations that we are interested to form 'part_ny_noaa' data. In 'part_ny_noaa' data, we focus on data between 2005 and 2010, and cleared missing data of tmax, tmin, and prcp. However, there are also so many observations, so that we set a random seed to help us random smapled 10000 observations in our 'part_ny_noaa'.


## Plotly box plot

```{r}
box_plot = part_ny_noaa %>%
  mutate(month = factor(month.name[month], levels = month.name)) %>%
  plot_ly(x = ~month, y = ~tmin, color = ~month, type = "box", colors = "viridis") %>%
  layout(title = "Boxplot of Minimum Temperature Distribution in each month", 
         legend = list(title = list(text = "<month>"))) #add title and lengend title in the graph

box_plot

```

This boxplot shows Minimum Temperature Distribution in each month during 2005-2010. It shows the possible minimum temperature range in each month. We could conclude that, in New York, most cold season is from December to February.

## Plotly Scatter plot

```{r}
scatter_plot = part_ny_noaa %>%
  mutate(month = factor(month.name[month], levels = month.name)) %>%
  group_by(month) %>%
  summarise(mean_tmax = mean(tmax, na.rm = T)) %>% 
  plot_ly(x = ~ month, y = ~mean_tmax, color = ~month, type = "scatter", mode = "line", colors = "viridis") %>%
  layout(title = "Mean Maximum Temperature by month", 
         yaxis = list(title = "mean of maximum temperature")) #add title in the graph

scatter_plot

```

This line plot shows mean maximum temperature in each month during 2005-2010. This result is consistent with the result of minimum temperature.  We could conclude that, in New York, the hottest time of year is during June-August.

## Plotly bar plot

```{r}
bar_plot = part_ny_noaa %>%
  mutate(month = factor(month.name[month], levels = month.name)) %>%
  group_by(month) %>%
  summarise(mean_prcp = mean(prcp, na.rm = T)) %>% 
  plot_ly(x = ~ month, y = ~mean_prcp, color = ~month, type = "bar", colors = "viridis") %>%
  layout(title = "Mean Precipitation (tenths of mm) in each month", 
         yaxis = list(title = "Mean of Precipitation")) #add title in the graph

bar_plot

```

This figure shows mean precipitation (tenths of mm) in each month during 2005-2010. We could find compared with January to May, there are more precipitation after June averagely. There are most precipitation in June, July, and October.

## Dashboard
Created a flexdashboard to show the plots, please visit [Dashboard](dashboard.html)
